Appendix B

### 2021-11-05 manuscript.Rmd
Minor change with subset command

## Merge "0"s and "1"s into "1"s select,subset assign)
descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
EFA.descriptives <- descriptives.data[1:428,]
CFA.descriptives <- descriptives.data[429:690, ]

>>>>

## Merge "0"s and "1"s into "1"s select,subset assign)
descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
#EFA.descriptives <- descriptives.data[1:428,]
EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
#CFA.descriptives <- descriptives.data[429:690, ]
CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
